Continuous Generalization of Buildings \protect\\ by Growing and Merging

### 2017-08-30 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
finished the descriptions of figures/Shrink_Erosion.pdf and figures/Shrink_Simplification.pdf

\usepackage{mathptmx}       % selects Times Roman as basic font
\usepackage{helvet}         % selects Helvetica as sans-serif font
\usepackage{courier}        % selects Courier as typewriter font
\usepackage{type1cm}        % activate if the above 3 fonts are
                            % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage[]{graphicx}
%\usepackage[draft]{graphicx}        % standard LaTeX graphics tool
\usepackage[size=small,labelfont=bf]{caption}
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom
\usepackage{pdflscape}
%\usepackage{rotating}
\usepackage{afterpage}
%\usepackage[disable]{todonotes}
\usepackage[colorinlistoftodos,prependcaption]{todonotes}
%\usepackage{todonotes}
\usepackage{subfigure}
\usepackage{setspace}
\usepackage{epstopdf}
\usepackage{flafter} %make sure that the floats are not placed 
%before their definition
\usepackage{times}
\usepackage{bm}
\usepackage{gensymb}  % for degree sign, e.g., temperature
\usepackage{amsmath}
\usepackage{amstext}
\usepackage{array}  %for define the fomats of columns in a table
\usepackage{dcolumn}
\usepackage[T1]{fontenc}
\usepackage{pgfplots}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{capt-of}
%\usepackage{marginnote}
\usepackage{xargs}   % Use more than one 
%optional parameter in a new commands
%\usepackage{siunitx} %for scientific 
%notation
%%we do this because of a bug of package floatrow
%\let\tmp\newinsert
%\let\newinsert\newbox
%\usepackage{floatrow}
%\let\newinsert\tmp
\usepackage{enumitem} %make items indent when using 
%\begin{enumerate}[(a)]
\usepackage{verbatimbox}  %for \addvbuffer
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{xspace}
%\usepackage{pdfcomment}
%\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
%		\node[shape=circle,draw,inner sep=1pt] (char) {#1};}}
%\newcommand*\circledtwo[1]{\tikz[baseline=(char.base)]{
%		\node[shape=circle,draw,inner sep=0.1pt] (char) {#1};}}
 \newcommand{\maps}{\ensuremath{M_\mathrm{s}}\xspace}
 \newcommand{\mapg}{\ensuremath{M_\mathrm{g}}\xspace}

@@

\todo[inline]{a brief introduction of our method.}
We name our input map as start map \maps,
and denote the scale of the start maps by $1:S_\mathrm{s}$.
We generate goal map \mapg at scale $1:S_\mathrm{g}$ 
($S_\mathrm{g} > S_\mathrm{s}$) by generalizing \maps. 
We use time $t\in[0,1]$ to define the continuous generalization
process. 
We require that the generalization yields exactly \maps when $t=0$, 
\mapg when $t=1$, 
and that \maps is continuously generalized into \mapg 
when $t$ increases from~$0$ to~$1$.
We define a simple function between scale and time, that is,
$S_t= S_\mathrm{s} + t(S_\mathrm{g}-S_\mathrm{s})$.

\subsection{Grow based on buffering}
\label{sec:Grow}
We grow building based on buffering. 
There are two typical ways of buffering polygons, i.e.,
one with round joins and the other with miter joins (see 
\fig\ref{fig:Buffer_TwoKinds}).
As buildings are usually rectangles, 
we choose the second way because it is 
better at keeping the right angles.
If an angle is acute, however, an excessively long \emph{spike} will be 
produced.
This spike may go across other buildings 
(see \fig\ref{fig:Buffer_MiterLimits}~(a)).
To avoid this kind of interruptions, 
we require that for an angle if a vertex of the 
buffer is more than $\alpha d_\mathrm{G} (\alpha \ge 1)$, 
where $d_\mathrm{G}$ is the growing distance, 
away from the original vertex, 
a \emph{square} joining is applied
(see \fig\ref{fig:Buffer_MiterLimits}~(b)).
To keep right angles of buildings, 
we must have $\alpha \geq \sqrt{2}$. 
We set $\alpha  = 1.5$ so that a square joining is applied when an angle is 
smaller than $83.6 \degree$.

@@

The area of a building on map should be at least $a\,\mathrm{mm}^2$ so that the 
building is large enough to be perceived.
In \sect\ref{sec:Simplify}, we show that we set $a=4$.
Accordingly, a square at the start map should have 
area $a S_\mathrm{s}^2\,\mathrm{mm}^2$ at least, and
a square at the goal map should have 
area $a S_\mathrm{g}^2\,\mathrm{mm}^2$ at least.
The difference of the side lengths is 
$\sqrt{a} (S_\mathrm{g}-S_\mathrm{s})\,\mathrm{mm}$ 
 (see \fig\ref{fig:Growth}).
A square on the start map needs to grow $\frac{1}{2}\sqrt{a} 
(S_\mathrm{g}-S_\mathrm{s})\,\mathrm{mm}$ so that 
it can survive when users zoom out from 
the start map to the goal map.
In order to eliminate small buildings, 
we define our growing distance as
\begin{equation}
\label{eq:d_G}
d_\mathrm{G}=\frac{\lambda}{2}\sqrt{a} (S_\mathrm{g}-S_\mathrm{s})\,\mathrm{mm} 
\quad 0 < \lambda <1,
\end{equation}
where variable $\lambda$ is a growing factor. 
A larger $\lambda$ results in  
fewer buildings to be eliminated, and vice versa.
During our growing, the growth at time $t$ is
\begin{equation}
\label{eq:d_Gt}
\dtrm{G} = t \cdot d_\mathrm{G}.
\end{equation}

@@

\subsection{Merge close buildings by introducing bridges}
The distance between two buildings should be larger than a threshold
\parencite{Regnauld2001,Li2004}.
Following \textcite{Basaraner2008,Stoter2009}, 
we set the separation threshold $\epsilon= 0.2\,\mathrm{mm}$ for target map. 
The separation threshold at time $t$ is
\begin{equation}
\label{eq:d_epsilont}
d_{\epsilon, t} = \epsilon \cdot S_t.
\end{equation}

@@

We would like to use $\dtrm{E}=\frac{l}{2} \cdot S_t$
(see \eq\ref{eq:d_epsilont}) so that
any pits and spikes narrower than $l$ will be removed. 
We set $l=0.3\,\mathrm{mm}$, which was used as a length threshold by 
\textcite{Regnauld2001,Li2004,Basaraner2008}.
According to \eq\ref{eq:d_Gt}, $\dtrm{G}$ can be arbitrarily small 
when $t$ is small, 
but $d_{\epsilon, t}$ is at least $\frac{l}{2} S_\mathrm{s}$. 
In this case, $\dtrm{G}-\dtrm{E} \le 0$ when $t$ is small, 
which violates \eq\ref{eq:d_Dt}, where $\dtrm{D}>0$.
As a compromise, we use
\begin{equation}
\label{eq:d_Et}
\dtrm{E} =t \cdot \frac{l}{2} S_\mathrm{g}.
\end{equation}
Still, we should make sure that $\dtrm{G}-\dtrm{E} > 0$, which means
$t \cdot \frac{\lambda}{2}\sqrt{a} (S_\mathrm{g}-S_\mathrm{s})-
t \cdot \frac{l}{2} S_\mathrm{g} >0$.
As a result, we should make sure that
\begin{equation}
\label{eq:S_g}
S_\mathrm{g} > \frac{\lambda\sqrt{a}}{\lambda\sqrt{a}-l} S_s.
\end{equation}

@@

After carrying out the buffering-based methods, 
we simplify the grown buildings using Imai--Iri algorithm 
\parencite{ImaiIri1988}.
This algorithm first finds all the valid shortcuts of a polyline.
A shortcut is valid for a segment 
if the distance between the segment and the shortcut is at most a specified 
value
(see \fig\ref{fig:ImaiIri_Shortcut}).
We set the value also as $l$. 
Second, the algorithm finds a sequence of valid shortcuts, from the beginning 
of a polyline to the end, using breadth-first search.
The sequence of valid shortcuts is an approximation of the polyline, 
and has the least number of line segments.

@@

\begin{figure}[tb]
	\centering
	\includegraphics[draft=false]{Shrink_Erosion}
	\caption{.
	}
	\label{fig:Shrink_Erosion}
\end{figure}

@@

\subsection{Text}
\label{sec:Formalizing}

>>>>

\usepackage{mathptmx}       % selects Times Roman as basic font
\usepackage{helvet}         % selects Helvetica as sans-serif font
\usepackage{courier}        % selects Courier as typewriter font
\usepackage{type1cm}        % activate if the above 3 fonts are
                            % not available on your system
%
\usepackage{makeidx}         % allows index generation
%\usepackage[]{graphicx}
\usepackage[draft]{graphicx}        % standard LaTeX graphics tool
\usepackage[size=small,labelfont=bf]{caption}
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom
\usepackage{pdflscape}
%\usepackage{rotating}
\usepackage{afterpage}
%\usepackage[disable]{todonotes}
\usepackage[colorinlistoftodos,prependcaption]{todonotes}
%\usepackage{todonotes}
\usepackage{subfigure}
\usepackage{setspace}
\usepackage{epstopdf}
\usepackage{flafter} %make sure that the floats are not placed 
%before their definition
\usepackage{times}
\usepackage{bm}
\usepackage{gensymb}  % for degree sign, e.g., temperature
\usepackage{amsmath}
\usepackage{amstext}
\usepackage{array}  %for define the fomats of columns in a table
\usepackage{dcolumn}
\usepackage[T1]{fontenc}
\usepackage{pgfplots}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{capt-of}
%\usepackage{marginnote}
\usepackage{xargs}   % Use more than one 
%optional parameter in a new commands
%\usepackage{siunitx} %for scientific 
%notation
%%we do this because of a bug of package floatrow
%\let\tmp\newinsert
%\let\newinsert\newbox
%\usepackage{floatrow}
%\let\newinsert\tmp
\usepackage{enumitem} %make items indent when using 
%\begin{enumerate}[(a)]
\usepackage{verbatimbox}  %for \addvbuffer
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{xspace}
%\usepackage{pdfcomment}
%\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
%		\node[shape=circle,draw,inner sep=1pt] (char) {#1};}}
%\newcommand*\circledtwo[1]{\tikz[baseline=(char.base)]{
%		\node[shape=circle,draw,inner sep=0.1pt] (char) {#1};}}
 \newcommand{\maps}{\ensuremath{M_\mathrm{s}}\xspace}
 \newcommand{\mapg}{\ensuremath{M_\mathrm{g}}\xspace}

@@

\todo[inline]{a brief introduction of our method.}
We name our input map as start map,
and denote the scale of the start map by $1:M_\mathrm{s}$.
We generate a goal map \mapg at scale $1:M_\mathrm{g}$ 
($M_\mathrm{g} > M_\mathrm{s}$) by generalizing the start map. 
We use time $t\in[0,1]$ to define the continuous generalization
process. 
We require that the generalization yields exactly the start map when $t=0$, 
the goal map when $t=1$, 
and that the start map is continuously generalized into the goal map 
when $t$ increases from~$0$ to~$1$.
For the sake of convenience, we define parameter
$M_t= M_\mathrm{s} + t \cdot (M_\mathrm{g}-M_\mathrm{s})$.

\subsection{Grow based on buffering}
\label{sec:Grow}
We grow building based on buffering. 
There are two typical ways of buffering polygons, i.e.,
one with round joins and the other with miter joins (see 
\fig\ref{fig:Buffer_TwoKinds}).
As buildings are usually rectangles, 
we choose the second way because it is 
better at keeping the right angles.
If an angle is acute, however, an excessively long \emph{spike} will be 
produced.
This spike may go across other buildings 
(see \fig\ref{fig:Buffer_MiterLimits}~(a)).
To avoid this kind of interruptions, 
we require that for an angle if a vertex of the 
buffer is more than $\alpha d_\mathrm{G} (\alpha \ge 1)$, 
where $d_\mathrm{G}$ is the growing distance, 
away from the original vertex, 
a \emph{square} joining is applied
(see \fig\ref{fig:Buffer_MiterLimits}~(b)).
To keep right angles of buildings, 
we must have $\alpha \geq \sqrt{2}$. 
We set $\alpha  = 1.5$ so that a square joining is applied when an angle is 
smaller (more acute) than $83.6 \degree$.

@@

The area of a building on map should be at least $a\,\mathrm{mm}^2$ so that the 
building is large enough to be perceived.
In \sect\ref{sec:Simplify}, we show that we set $a=4$.
Accordingly, a square at the start map should have 
area $a M_\mathrm{s}^2\,\mathrm{mm}^2$ at least, and
a square at the goal map should have 
area $a M_\mathrm{g}^2\,\mathrm{mm}^2$ at least.
The difference of the side lengths is 
$\sqrt{a} (M_\mathrm{g}-M_\mathrm{s})\,\mathrm{mm}$ 
 (see \fig\ref{fig:Growth}).
A square on the start map needs to grow $\frac{1}{2}\sqrt{a} 
(M_\mathrm{g}-M_\mathrm{s})\,\mathrm{mm}$ so that 
it can survive when users zoom out from 
the start map to the goal map.
In order to eliminate small buildings, 
we define our growing distance as
\begin{equation}
\label{eq:d_G}
d_\mathrm{G}=\frac{\lambda}{2}\sqrt{a} (M_\mathrm{g}-M_\mathrm{s})\,\mathrm{mm} 
\quad 0 < \lambda <1,
\end{equation}
where variable $\lambda$ is a growing factor. 
A larger $\lambda$ results in  
fewer buildings to be eliminated, and vice versa.
During our growing, the growth at time $t$ is
\begin{equation}
\label{eq:d_Gt}
\dtrm{G} = t \cdot d_\mathrm{G}.
\end{equation}

@@

\subsection{Merge close buildings by introducing bridges}
The distance between two buildings should be larger than a threshold
\parencite{Regnauld2001,Li2004}.
Following \textcite{Basaraner2008,Stoter2009}, 
we set the separation threshold $\epsilon= 0.2\,\mathrm{mm}$ for target map. 
The separation threshold at time $t$ is
\begin{equation}
\label{eq:d_epsilont}
d_{\epsilon, t} = \epsilon \cdot M_t.
\end{equation}

@@

We would like to use $\dtrm{E}=\frac{l}{2} \cdot M_t$
(see \eq\ref{eq:d_epsilont}) so that
any pits and spikes narrower than $l$ will be removed. 
We set $l=0.3\,\mathrm{mm}$, which was used as a length threshold by 
\textcite{Regnauld2001,Li2004,Basaraner2008}.
According to \eq\ref{eq:d_Gt}, $\dtrm{G}$ can be arbitrarily small 
when $t$ is small, 
but $d_{\epsilon, t}$ is at least $\frac{l}{2} M_\mathrm{s}$. 
In this case, $\dtrm{G}-\dtrm{E} \le 0$ when $t$ is small, 
which violates \eq\ref{eq:d_Dt}, where $\dtrm{D}>0$.
As a compromise, we use
\begin{equation}
\label{eq:d_Et}
\dtrm{E} =t \cdot \frac{l}{2} M_\mathrm{g}.
\end{equation}
Still, we should make sure that $\dtrm{G}-\dtrm{E} > 0$, which means
$t \cdot \frac{\lambda}{2}\sqrt{a} (M_\mathrm{g}-M_\mathrm{s})-
t \cdot \frac{l}{2} M_\mathrm{g} >0$.
As a result, we should make sure that
\begin{equation}
\label{eq:S_g}
M_\mathrm{g} > \frac{\lambda\sqrt{a}}{\lambda\sqrt{a}-l} S_s.
\end{equation}

@@

After carrying out the buffering-based methods, 
we simplify the grown buildings using Imai--Iri algorithm 
\parencite{ImaiIri1988}.
This algorithm first finds all the valid shortcuts of a polyline.
A shortcut is valid for a segment 
if the distance between the segment and the shortcut is at most a specified 
value
(see \fig\ref{fig:ImaiIri_Shortcut}).
We set the value also as $l$.
That is, at time $t$, the threshold distance is
\begin{equation}
\label{eq:d_lt}
d_{l,t}= l \cdot M_t.
\end{equation}
Second, the algorithm finds a sequence of valid shortcuts, from the beginning 
of a polyline to the end, using breadth-first search.
The sequence of valid shortcuts is an approximation of the polyline, 
and has the least number of line segments.

@@

\begin{figure}[tb]
	\centering
	\includegraphics[draft=false]{Shrink_Erosion}
	\caption{A building shrinks during growing because of dilation and erosion, 
	where $t_1=0.6$, $t_2=0.7$, and $t_3=1$.
		The small gray polygons represent the original building.
		(a) Grow and Dilate the building with distances $\dtrm[1]{G}$ and 
		$\dtrm[1]{D}$, respectively;
		(b) Erode the polygon in (a) with distance $\dtrm[1]{D} + \dtrm[1]{E}$;
		(c) Dilate the polygon in (b) with distance $\dtrm[1]{E}$.
		(d) The large gray polygon is the target shape on goal map.
		The process for (e), (f), and (g) is the same as the process of (a), 
		(b), and (c).
		The darker gray piece in (g) shows 
		the part which is included in the grown polygon of (c), 
		but not in the grown polygon of (g).
	}
	\label{fig:Shrink_Erosion}
\end{figure}

\begin{figure}[tb]
	\centering
	\includegraphics[draft=false]{Shrink_Simplification}
	\caption{A building shrinks during growing because of line simplification, 
		where $t_1=0.7$, $t_2=0.8$, and $t_3=1$.
		The small gray polygons represent the original building.
		The process for (a), (b), and (c), and 
		the process for (e), (f), and (g) are the same as 
		the processes in \fig\ref{fig:Shrink_Erosion}.
		(d) The large gray polygon is the target shape on goal map.
		(h) Simplify the polygon in (g) using the Imai--Iri algorithm.
		Note that $d_{l,t_1}<d_{l,t_2}$ see \eq\ref{eq:d_lt}),
		which is why the Imai--Iri algorithm does not 
		remove any point of the polygon in (c),
		but removes two points of the polygon in (g).
		The darker gray pieces in (h) show 
		the parts which are included in the polygon of (c), 
		but not in the polygon of (h).
	}
	\label{fig:Shrink_Simplification}
\end{figure}

@@

The area on start map is $some number\,\text{mm}^2$.
Our area on map is $some number\,\text{mm}^2$.
According to \eq4 of paper \textcite{Topfer1966}, 
the area on map should be $some number\,\text{mm}^2$
